---
title: "Mapping food system institutions and policies in Niger"
author: "Hema Aboubacar & Srivastava  Nandita"
date: '`r format (Sys.Date(), "%d %B %Y")`'
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
---


```{r setup, include = FALSE, warning=FALSE, echo = FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(officedown)
library(officer)
library(gtsummary)
library(flextable)
library(magrittr)

set_gtsummary_theme(theme_gtsummary_compact())

######### Create default BioAVR table from dataframe
#
# Dependencies : dplyr, flextable, officer
# source link : https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/
customtab_defaults <- function(){
set_flextable_defaults(font.family = "Calibri",
font.size = 10,
border.color = "black")
}
custom_tab <- function(df, header, footer){
flextable(df) %>%
add_header_lines(header) %>%
add_footer_lines(footer) %>%
bold(i = 1, part = "header") %>%
hline_top(part = "header",
border = fp_border(color = "green",
width = 3,
style = "solid")) %>%
hline(i = 1,
part = "header",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_top(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "footer",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
border_inner_h(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "dotted")) %>%
autofit(part = "body") %>%
bg(part = "body", bg = "#f5f5f5") %>%
align(part = "all", align = "center") %>%
align(j = 1, part = "all", align = "left")
}
```


<!---BLOCK_TOC--->

\newpage

```{r}
library(dplyr)
library(expss)
library(openxlsx)
library(readxl)
library(tidyverse)
library(janitor)

library(data.table)
library(stringr)
library(compareDF)
library(sjlabelled)
library(lmtest)
library(sandwich)
library(labelled)

```

```{r echo=F}
# This function aims at providing customized statistics in the table that 
# with be produced using the gtsummary package
# Basically the gtsummary does not include such a function 
add_by_n <- function(data, variable, by, tbl, ...) {
  data %>%
    select(all_of(c(variable, by))) %>%
    dplyr::group_by(.data[[by]]) %>%
    dplyr::summarise_all(~sum(!is.na(.))) %>%
    rlang::set_names(c("by", "variable")) %>%
    dplyr::left_join(
      tbl$df_by %>% select(by, by_col),
      by = "by"
    ) %>%
    mutate(
      by_col = paste0("add_n_", by_col),
      variable = style_number(variable)
    ) %>%
    select(-by) %>%
    tidyr::pivot_wider(names_from = by_col, 
                       values_from = variable)
}

```

<!---BLOCK_LANDSCAPE_START--->

```{r}
library(haven)
EVALUATION_DES_CAPACITES_Hema <- read_dta(paste0(here::here(),"/data/IFPRI NIGER - EVALUATION DES CAPACITES_Hema.dta"))
domain = c("dom_1","dom_2","dom_3","dom_4","dom_5")
attach(EVALUATION_DES_CAPACITES_Hema)
```

```{r}
# //Organizational capacity
#  
# dtable, factor (q_iii_25 q_iii_30 q_iii_35) // enabling environment and org capacity
# dtable, factor (q_iv_1 q_iv_5) // Analysis
# dtable, factor (q_v_1 q_v_5) // strategy development 
# dtable, factor (q_vi_1 q_vi_5 q_vi_9) // implementation 
# dtable, factor (q_vii_1 q_vii_5 q_vii_9 q_vii_11 q_vii_10 q_vii_15 q_vii_19 q_vii_21 q_vii_23) // M&E
# dtable, factor (q_viii_1 q_viii_5 q_viii_9) // strategy revision
# dtable, factor (q_ix_1 q_ix_5 q_ix_11 q_ix_15 q_ix_22) // institutional motivation
# dtable, factor (q_x_1 q_x_4 q_x_6 q_x_8) // operational capacity
#  
# //Individual capacity
#  
# dtable, factor (q_xi_2_1 q_xi_2_2 q_xi_2_3 q_xi_2_4 q_xi_2_5) // individual capacity//
```

# Organizational capacity

## Enabling environment and organization capacity


```{r}
var_vec = c("q_iii_25"
)
# EVALUATION_DES_CAPACITES_Hema = EVALUATION_DES_CAPACITES_Hema %>% dplyr::mutate(q_iii_25 = dplyr::recode(q_iii_25, `1` = 1,`2` =1 ,`3`= 2, `4`= 3,`5`= 3))
# EVALUATION_DES_CAPACITES_Hema <- EVALUATION_DES_CAPACITES_Hema %>% 
#   dplyr::mutate(across(var_vec,
#                 ~recode(.,
#                   "1" = 1,"2" =1 ,"3"= 2, "4"= 3,"5"= 3
#                 
#                 )
#   )
#   )
# 
# EVALUATION_DES_CAPACITES_Hema <- EVALUATION_DES_CAPACITES_Hema %>% 
#   dplyr::mutate(across(var_vec,
#                 ~labelled::labelled(., labels = c(
#                   Agree = 1,Neutral = 2,Disagree =3
#                 )
#                 )
#   )
#  )
# EVALUATION_DES_CAPACITES_Hema$q_iii_25 <- labelled::labelled(EVALUATION_DES_CAPACITES_Hema$q_iii_25, c(Agree = 1,Neutral = 2,Disagree =3))

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
   labelled::to_factor()
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
                df_2,
                df_3,
                df_4,
                df_5)

names(df_fc)=c("Leadership is responsive, inspiring and sensitive",
               "All",
                 "Nutrition, health, and food, security",
                 "Poverty reduction, livelihoods, and jobs",
                 "Gender equality, youth, and social inclusion",
                 "Climate adaptation and mitigation",
                 "Environmental health and biodiversity"
)

# hs <- createStyle(
#   textDecoration = "BOLD", fontColour = "#FFFFFF", fontSize = 12,
#   fontName = "Arial Narrow", fgFill = "#4F80BD"
# )
# 
# write.xlsx(df_fc,
#            file = "Tables Ability to evaluate.xlsx",
#            colNames = TRUE, borders = "rows", headerStyle = hs, sheetName = "Ability to evaluate", append=TRUE
# )

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_iii_30"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("Leaders of the policy process organisations provide appropriate strategic guidance (strategic leader, operational leader, or both)",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_iii_35"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("Vision, mission and strategies are regularly discussed within your organization",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```





\newpage

## Analysis

```{r}
var_vec = c("q_iv_1"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("There is a linked network of private, public, nonprofit, and academic researchers, which your organization is a part of, that hold each other accountable for unbiased evidence generation in your sector",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_iv_5"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("There is strong interdisciplinary research connections (eg. Agriculture, nutrition, environment)",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Strategy development 

```{r}
var_vec = c("q_v_1"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("Policies/ strategies are developed through a participatory and consultative process with multiple opportunities to obtain stakeholder and public input that yields evidence-based solutions.",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_v_5"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("The policy/strategy development process is transparent and evidence-based, reflecting the vulnerabilities of the country's food system and the means to transform it.",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Implementation 

```{r}
var_vec = c("q_vi_1"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("To ensure effective implementation at local level, there is a strong decentralized capacity () and clear communication channels between the different administrative levels.",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vi_5"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("The capacity to implement institutional policy changes at sector level is sufficient.",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vi_9"
)


df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("There is an effective and adaptable extension system, from local NGOs and the private sector, for sector-specific support.",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## M&E

```{r}
# q_vii_1 q_vii_5 q_vii_9 q_vii_11 q_vii_10 q_vii_15 q_vii_19 q_vii_21 q_vii_23
```

```{r}
var_vec = c("q_vii_1"
)

var_lab = c("Monitoring and evaluation data on policy achievements and results are available and integrated into the national statistics collection system.")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_5"
)

var_lab = c("Data are collected to predict and monitor shocks or threats to food systems")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_9"
)

var_lab = c("Monitoring and evaluation of the production process, from farmer to consumer, are integrated into the agricultural research system
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_11"
)

var_lab = c(" Sectoral reviews are carried out and other research data collected in order to effectively evaluate the effects of the products and services provided (outcomes) with a view to developing future strategies.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_10"
)

var_lab = c("Activities, outputs, outcomes and performance indicators are effectively evaluated through monitoring and evaluation activities to address programs and policies related to the transformation of food systems.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


```{r}
var_vec = c("q_vii_15"
)

var_lab = c("The internal management and evaluation of your organization stimulates frequent critical reflection, enabling you to learn from your mistakes.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


```{r}
var_vec = c("q_vii_19"
)

var_lab = c("Members/staff of your organization are free to propose ideas for implementing food systems transformation.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_21"
)

var_lab = c("Your organization has an effective system for keeping in touch with general trends and developments related to food systems.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_vii_23"
)

var_lab = c("Your organization is open and responsive to its stakeholders and the general public.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Strategy revision

```{r}
#q_viii_1 q_viii_5 q_viii_9
```

```{r}
var_vec = c("q_viii_1"
)

var_lab = c("The decentralization of powers is sufficient for strategies to be immediately adapted or revised to suit the local context.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_viii_5"
)

var_lab = c("There is a capacity to analyze and develop commercial and institutional strategies dictated by control system data.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_viii_9"
)

var_lab = c("There is a capacity to develop revisions of policy strategies based on the effects of shocks on food production systems.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Institutional motivation

```{r}
#q_ix_1 q_ix_5 q_ix_11 q_ix_15 q_ix_22
```

```{r}
var_vec = c("q_ix_1"
)

var_lab = c("The turnover of members or staff in your organization is relatively low.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_ix_5"
)

var_lab = c("The members or staff of your organization have the necessary skills to use reliable data for strategic analysis and other policy-related work.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_ix_11"
)

var_lab = c("Appropriate incentives are in place to support member or staff motivation
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_ix_15"
)

var_lab = c("Funding from multiple sources is sufficient to cover the cost of operations.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_ix_22"
)

var_lab = c("There is a strong capacity to communicate and share research results with government agencies, farmers, the private sector and other stakeholders.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Operational capacity

```{r}
#q_x_1 q_x_4 q_x_6 q_x_8
```

```{r}
var_vec = c("q_x_1"
)

var_lab = c("Your organization has clear operational plans for achieving its mandate and objectives, which are fully understood by all members/staff.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_x_4"
)

var_lab = c("Your organization delivers the expected results on time.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_x_6"
)

var_lab = c(" Staff Are able to implement your organization's operational plans")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_x_8"
)

var_lab = c("Your organization has mechanisms in place to verify that its services meet the needs of customers, stakeholders or beneficiaries.
            ")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


## Individual capacity

```{r}
#q_xi_2_1 q_xi_2_2 q_xi_2_3 q_xi_2_4 q_xi_2_5
```

```{r}
var_vec = c("q_xi_2_1"
)

var_lab = c("Capacity to produce and use information")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_xi_2_2"
)

var_lab = c("Ability to conceptualize problems and potential solutions")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_xi_2_3"
)

var_lab = c("Research and development capacity")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

```{r}
var_vec = c("q_xi_2_4"
)

var_lab = c("Capacity to communicate, popularize and disseminate information")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage


```{r}
var_vec = c("q_xi_2_5"
)

var_lab = c("Other ( specify)")

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No"))  %>%
  labelled::to_factor() 
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "categorical"),
              statistic = list(all_categorical() ~ "{n}({p}%)"),
              digits = everything() ~ c(0,1), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("label","stat_0","stat_2")] %>% slice(-1)
df_2=tb_2$table_body[,c("stat_2")] %>% slice(-1)
df_3=tb_3$table_body[,c("stat_2")] %>% slice(-1)
df_4=tb_4$table_body[,c("stat_2")] %>% slice(-1)
df_5=tb_5$table_body[,c("stat_2")] %>% slice(-1)

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

header <- str_squish(str_remove("Table : ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)

```

\newpage

