---
title: "Mapping food system institutions and policies in Niger"
author: "Hema Aboubacar & Srivastava  Nandita"
date: '`r format (Sys.Date(), "%d %B %Y")`'
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
---


```{r setup, include = FALSE, warning=FALSE, echo = FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(officedown)
library(officer)
library(gtsummary)
library(flextable)
library(magrittr)

set_gtsummary_theme(theme_gtsummary_compact())

######### Create default BioAVR table from dataframe
#
# Dependencies : dplyr, flextable, officer
# source link : https://www.r-bloggers.com/2021/11/publication-ready-tables-with-flextable-and-own-theme-in-r/
customtab_defaults <- function(){
set_flextable_defaults(font.family = "Calibri",
font.size = 10,
border.color = "black")
}
FitFlextableToPage <- function(ft, pgwidth = 7){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}
custom_tab <- function(df, header, footer){
flextable(df) %>%
add_header_lines(header) %>%
add_footer_lines(footer) %>%
bold(i = 1, part = "header") %>%
hline_top(part = "header",
border = fp_border(color = "green",
width = 3,
style = "solid")) %>%
hline(i = 1,
part = "header",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_top(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
hline_bottom(part = "footer",
border = fp_border(color = "black",
width = 0.25,
style = "solid")) %>%
border_inner_h(part = "body",
border = fp_border(color = "black",
width = 0.25,
style = "dotted")) %>%
autofit(part = "body") %>%
bg(part = "body", bg = "#f5f5f5") %>%
align(part = "all", align = "center") %>%
align(j = 1, part = "all", align = "left")
}
```


<!---BLOCK_TOC--->

\newpage

```{r}
library(dplyr)
library(expss)
library(openxlsx)
library(readxl)
library(tidyverse)
library(janitor)

library(data.table)
library(stringr)
library(compareDF)
library(sjlabelled)
library(lmtest)
library(sandwich)
library(labelled)

```

```{r echo=F}
# This function aims at providing customized statistics in the table that 
# with be produced using the gtsummary package
# Basically the gtsummary does not include such a function 
add_by_n <- function(data, variable, by, tbl, ...) {
  data %>%
    select(all_of(c(variable, by))) %>%
    dplyr::group_by(.data[[by]]) %>%
    dplyr::summarise_all(~sum(!is.na(.))) %>%
    rlang::set_names(c("by", "variable")) %>%
    dplyr::left_join(
      tbl$df_by %>% select(by, by_col),
      by = "by"
    ) %>%
    mutate(
      by_col = paste0("add_n_", by_col),
      variable = style_number(variable)
    ) %>%
    select(-by) %>%
    tidyr::pivot_wider(names_from = by_col, 
                       values_from = variable)
}

```

<!---BLOCK_LANDSCAPE_START--->

```{r}
library(haven)
EVALUATION_DES_CAPACITES_Hema <- read_dta(paste0(here::here(),"/data/IFPRI NIGER - EVALUATION DES CAPACITES_Hema.dta"))
domain = c("dom_1","dom_2","dom_3","dom_4","dom_5")
attach(EVALUATION_DES_CAPACITES_Hema)
```

```{r}
# Text analysis

# q_xi_2_1_* // capacity to produce and use information
# q_xi_2_2_* // ability to conceptualize problems
# q_xi_2_3_* // R&D
# q_xi_2_4_* // communicate, popularize, disseminate
# q_xi_2_5_* // other
```

# Organizational capacity

## Weakness of political leadership

```{r}
var_vec = c("q_iii_28_1",
            "q_iii_28_2",
            "q_iii_28_3",
            "q_iii_28_4",
            "q_iii_28_5",
            "q_iii_28_6",
            "q_iii_28_7",
            "q_iii_28_8",
            "q_iii_28_96"
)
var_lab = c("Weakness of political leadership
            ")
label_vec = c("Vulnerability to climatic factors",
              "Soil degradation and pressure on natural resources",
              "Fragility and conflict",
              "Limited agricultural education",
              "Dependence on food aid",
              "Problems of governance and corruption hamper the effectiveness of food and agricultural programs, and the equitable distribution of resources.",
              "Persistent social inequalities, such as access to land and resources",
              "Limited access to data and information",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))

description = tibble(
  name = var_vec,
  label = label_vec
)
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%
  set_variable_labels(.labels = var_labels, .strict = FALSE)

```



```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```


```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)


# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
ft = custom_tab(df_fc, header, footer)
#FitFlextableToPage(ft)
ft
```

\newpage

## Weakness in strategic direction by manager

```{r}
var_vec = c("q_iii_33_1",
            "q_iii_33_2",
            "q_iii_33_3",
            "q_iii_33_4",
            "q_iii_33_5",
            "q_iii_33_6",
            "q_iii_33_96"
)
var_lab = c("Weakness in strategic direction by manager
            ")
label_vec = c("Lack of human and institutional capacity to design, implement and monitor food and agricultural programs",
              "Dependence on food aid and international assistance to meet food challenges",
              "Persistent social inequalities, such as access to land and resources, complicate the implementation of equitable initiatives for all groups in society.",
              "Poor transport infrastructure and limited access to markets hamper marketing opportunities for farmers.",
              "Security and fragility challenges disrupt food production and agricultural activities",
              "Lack of reliable, up-to-date data hampers evidence-based planning and decision-making.",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))

description = tibble(
  name = var_vec,
  label = label_vec
)
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%
  set_variable_labels(.labels = var_labels, .strict = FALSE)

```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```


```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)


# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
ft = custom_tab(df_fc, header, footer)
#FitFlextableToPage(ft)
ft
```

\newpage

## Gaps/changes needed at the policy level

```{r}
set_gtsummary_theme(theme_gtsummary_compact())
var_lab = c("Gaps/changes needed at the policy level")
tb_gaps_dom_1=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_1,
                                                               q_ii_9_1_1,
                                                               q_ii_9_2_1,
                                                               q_ii_9_3_1,
                                                               q_ii_9_4_1,
                                                               q_ii_9_5_1,
                                                               q_ii_9_6_1,
                                                               q_ii_9_7_1,
                                                               # q_ii_9_8_1,
                                                               # q_ii_9_9_1,
                                                               # q_ii_9_10_1,
                                                               q_ii_9_96_1
) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_9"), as.numeric)) %>% 
  apply_labels(q_ii_9_1_1 = "Lack of coordination",
               q_ii_9_2_1 = "Unequal access",
               q_ii_9_3_1 = "Food industry lobbying",
               q_ii_9_4_1 = "Focus on production rather than nutrition",
               q_ii_9_5_1 = "Pressure on natural resources",
               q_ii_9_6_1 = "Lack of public awareness",
               q_ii_9_7_1 = "Short-term vision",
               # q_ii_9_8_1 = "Bureaucratic inefficiency",
               # q_ii_9_9_1 = "Lack of financial resources",
               # q_ii_9_10_1 = "Resistance to change",
               q_ii_9_96_1 = "Other ( specify)"
  ) %>%  
  tbl_summary(by = dom_1, 
              type= (list=c(q_ii_9_1_1,
                            q_ii_9_2_1,
                            q_ii_9_3_1,
                            q_ii_9_4_1,
                            q_ii_9_5_1,
                            q_ii_9_6_1,
                            q_ii_9_7_1,
                            # q_ii_9_8_1,
                            # q_ii_9_9_1,
                            # q_ii_9_10_1,
                            q_ii_9_96_1) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),#
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_gaps_dom_2=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_2,
                                                               q_ii_9_1_2,
                                                               q_ii_9_2_2,
                                                               q_ii_9_3_2,
                                                               q_ii_9_4_2,
                                                               q_ii_9_5_2,
                                                               q_ii_9_6_2,
                                                               q_ii_9_7_2,
                                                               # q_ii_9_8_2,
                                                               # q_ii_9_9_2,
                                                               # q_ii_9_10_2,
                                                               q_ii_9_96_2
) %>% 
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_9"), as.numeric)) %>% 
  apply_labels(q_ii_9_1_2 = "Lack of coordination",
               q_ii_9_2_2 = "Unequal access",
               q_ii_9_3_2 = "Food industry lobbying",
               q_ii_9_4_2 = "Focus on production rather than nutrition",
               q_ii_9_5_2 = "Pressure on natural resources",
               q_ii_9_6_2 = "Lack of public awareness",
               q_ii_9_7_2 = "Short-term vision",
               # q_ii_9_8_2 = "Bureaucratic inefficiency",
               # q_ii_9_9_2 = "Lack of financial resources",
               # q_ii_9_10_2 = "Resistance to change",
               q_ii_9_96_2 = "Other ( specify)"
  ) %>%  
  tbl_summary(by = dom_2, 
              type= (list=c(q_ii_9_1_2,
                            q_ii_9_2_2,
                            q_ii_9_3_2,
                            q_ii_9_4_2,
                            q_ii_9_5_2,
                            q_ii_9_6_2,
                            q_ii_9_7_2,
                            # q_ii_9_8_2,
                            # q_ii_9_9_2,
                            # q_ii_9_10_2,
                            q_ii_9_96_2) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_gaps_dom_3=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_3,
                                                               q_ii_9_1_3,
                                                               q_ii_9_2_3,
                                                               q_ii_9_3_3,
                                                               q_ii_9_4_3,
                                                               q_ii_9_5_3,
                                                               q_ii_9_6_3,
                                                               q_ii_9_7_3,
                                                               # q_ii_9_8_3,
                                                               # q_ii_9_9_3,
                                                               # q_ii_9_10_3,
                                                               q_ii_9_96_3
) %>% 
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_9"), as.numeric)) %>% 
  apply_labels(q_ii_9_1_3 = "Lack of coordination",
               q_ii_9_2_3 = "Unequal access",
               q_ii_9_3_3 = "Food industry lobbying",
               q_ii_9_4_3 = "Focus on production rather than nutrition",
               q_ii_9_5_3 = "Pressure on natural resources",
               q_ii_9_6_3 = "Lack of public awareness",
               q_ii_9_7_3 = "Short-term vision",
               # q_ii_9_8_3 = "Bureaucratic inefficiency",
               # q_ii_9_9_3 = "Lack of financial resources",
               # q_ii_9_10_3 = "Resistance to change",
               q_ii_9_96_3 = "Other ( specify)"
  ) %>%  
  tbl_summary(by = dom_3, 
              type= (list=c(q_ii_9_1_3,
                            q_ii_9_2_3,
                            q_ii_9_3_3,
                            q_ii_9_4_3,
                            q_ii_9_5_3,
                            q_ii_9_6_3,
                            q_ii_9_7_3,
                            # q_ii_9_8_3,
                            # q_ii_9_9_3,
                            # q_ii_9_10_3,
                            q_ii_9_96_3) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```
```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_gaps_dom_4=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_4,
                                                               q_ii_9_1_4,
                                                               q_ii_9_2_4,
                                                               q_ii_9_3_4,
                                                               q_ii_9_4_4,
                                                               q_ii_9_5_4,
                                                               q_ii_9_6_4,
                                                               q_ii_9_7_4,
                                                               # q_ii_9_8_4,
                                                               # q_ii_9_9_4,
                                                               # q_ii_9_10_4,
                                                               q_ii_9_96_4
) %>% 
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_9"), as.numeric)) %>% 
  apply_labels(q_ii_9_1_4 = "Lack of coordination",
               q_ii_9_2_4 = "Unequal access",
               q_ii_9_3_4 = "Food industry lobbying",
               q_ii_9_4_4 = "Focus on production rather than nutrition",
               q_ii_9_5_4 = "Pressure on natural resources",
               q_ii_9_6_4 = "Lack of public awareness",
               q_ii_9_7_4 = "Short-term vision",
               # q_ii_9_8_4 = "Bureaucratic inefficiency",
               # q_ii_9_9_4 = "Lack of financial resources",
               # q_ii_9_10_4 = "Resistance to change",
               q_ii_9_96_4 = "Other ( specify)"
  ) %>%  
  tbl_summary(by = dom_4, 
              type= (list=c(q_ii_9_1_4,
                            q_ii_9_2_4,
                            q_ii_9_3_4,
                            q_ii_9_4_4,
                            q_ii_9_5_4,
                            q_ii_9_6_4,
                            q_ii_9_7_4,
                            # q_ii_9_8_4,
                            # q_ii_9_9_4,
                            # q_ii_9_10_4,
                            q_ii_9_96_4) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```




```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_gaps_dom_5=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_5,
                                                               q_ii_9_1_5,
                                                               q_ii_9_2_5,
                                                               q_ii_9_3_5,
                                                               q_ii_9_4_5,
                                                               q_ii_9_5_5,
                                                               q_ii_9_6_5,
                                                               q_ii_9_7_5,
                                                               # q_ii_9_8_5,
                                                               # q_ii_9_9_5,
                                                               # q_ii_9_10_5,
                                                               q_ii_9_96_5
) %>% 
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_9"), as.numeric)) %>% 
  apply_labels(q_ii_9_1_5 = "Lack of coordination",
               q_ii_9_2_5 = "Unequal access",
               q_ii_9_3_5 = "Food industry lobbying",
               q_ii_9_4_5 = "Focus on production rather than nutrition",
               q_ii_9_5_5 = "Pressure on natural resources",
               q_ii_9_6_5 = "Lack of public awareness",
               q_ii_9_7_5 = "Short-term vision",
               # q_ii_9_8_5 = "Bureaucratic inefficiency",
               # q_ii_9_9_5 = "Lack of financial resources",
               # q_ii_9_10_5 = "Resistance to change",
               q_ii_9_96_5 = "Other ( specify)"
  ) %>%  
  tbl_summary(by = dom_5, 
              type= (list=c(q_ii_9_1_5,
                            q_ii_9_2_5,
                            q_ii_9_3_5,
                            q_ii_9_4_5,
                            q_ii_9_5_5,
                            q_ii_9_6_5,
                            q_ii_9_7_5,
                            # q_ii_9_8_5,
                            # q_ii_9_9_5,
                            # q_ii_9_10_5,
                            q_ii_9_96_5) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_gaps_dom_1=tb_gaps_dom_1$table_body[,c("var_label","stat_0","stat_2")]
df_gaps_dom_2=tb_gaps_dom_2$table_body[,c("stat_2")]
df_gaps_dom_3=tb_gaps_dom_3$table_body[,c("stat_2")]
df_gaps_dom_4=tb_gaps_dom_4$table_body[,c("stat_2")]
df_gaps_dom_5=tb_gaps_dom_5$table_body[,c("stat_2")]

df_fc = cbind(df_gaps_dom_1,
              df_gaps_dom_2,
              df_gaps_dom_3,
              df_gaps_dom_4,
              df_gaps_dom_5)


names(df_fc)=c(var_lab,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)


# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
ft = custom_tab(df_fc, header, footer)
#FitFlextableToPage(ft)
ft
```



\newpage

## Strengths of specific policies/programs

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_strengths_dom_1=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_1,
                                                                    q_ii_8_1_1,
                                                                    q_ii_8_2_1,
                                                                    q_ii_8_3_1,
                                                                    q_ii_8_4_1,
                                                                    q_ii_8_5_1,
                                                                    q_ii_8_6_1,
                                                                    # q_ii_8_7_1,
                                                                    # q_ii_8_8_1,
                                                                    # q_ii_8_9_1,
                                                                    q_ii_8_96_1
) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_8"), as.numeric)) %>% 
  apply_labels(q_ii_8_1_1 = "Coordination and collaboration",
               q_ii_8_2_1 = "Global vision",
               q_ii_8_3_1 = "Strategic direction",
               q_ii_8_4_1 = "Regulations and policies",
               q_ii_8_5_1 = "Public investment",
               q_ii_8_6_1 = "Mobilizing civil society",
               # q_ii_8_7_1 = "International food diplomacy",
               # q_ii_8_8_1 = "Education and awareness-raising",
               # q_ii_8_9_1 = "Innovation and adaptation",
               q_ii_8_96_1 = "Other ( specify )"
  ) %>%  
  tbl_summary(by = dom_1, 
              type= (list=c(q_ii_8_1_1,
                            q_ii_8_2_1,
                            q_ii_8_3_1,
                            q_ii_8_4_1,
                            q_ii_8_5_1,
                            q_ii_8_6_1,
                            # q_ii_8_7_1,
                            # q_ii_8_8_1,
                            # q_ii_8_9_1,
                            q_ii_8_96_1) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_strengths_dom_2=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_2,
                                                                    q_ii_8_1_2,
                                                                    q_ii_8_2_2,
                                                                    q_ii_8_3_2,
                                                                    q_ii_8_4_2,
                                                                    q_ii_8_5_2,
                                                                    q_ii_8_6_2,
                                                                    # q_ii_8_7_2,
                                                                    # q_ii_8_8_2,
                                                                    # q_ii_8_9_2,
                                                                    q_ii_8_96_2
) %>% 
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_8"), as.numeric)) %>% 
  apply_labels(q_ii_8_1_2 = "Coordination and collaboration",
               q_ii_8_2_2 = "Global vision",
               q_ii_8_3_2 = "Strategic direction",
               q_ii_8_4_2 = "Regulations and policies",
               q_ii_8_5_2 = "Public investment",
               q_ii_8_6_2 = "Mobilizing civil society",
               # q_ii_8_7_2 = "International food diplomacy",
               # q_ii_8_8_2 = "Education and awareness-raising",
               # q_ii_8_9_2 = "Innovation and adaptation",
               q_ii_8_96_2 = "Other ( specify )"
  ) %>%  
  tbl_summary(by = dom_2, 
              type= (list=c(q_ii_8_1_2,
                            q_ii_8_2_2,
                            q_ii_8_3_2,
                            q_ii_8_4_2,
                            q_ii_8_5_2,
                            q_ii_8_6_2,
                            # q_ii_8_7_2,
                            # q_ii_8_8_2,
                            # q_ii_8_9_2,
                            q_ii_8_96_2) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_strengths_dom_3=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_3,
                                                                    q_ii_8_1_3,
                                                                    q_ii_8_2_3,
                                                                    q_ii_8_3_3,
                                                                    q_ii_8_4_3,
                                                                    q_ii_8_5_3,
                                                                    q_ii_8_6_3,
                                                                    # q_ii_8_7_3,
                                                                    # q_ii_8_8_3,
                                                                    # q_ii_8_9_3,
                                                                    q_ii_8_96_3
) %>% 
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_8"), as.numeric)) %>% 
  apply_labels(q_ii_8_1_3 = "Coordination and collaboration",
               q_ii_8_2_3 = "Global vision",
               q_ii_8_3_3 = "Strategic direction",
               q_ii_8_4_3 = "Regulations and policies",
               q_ii_8_5_3 = "Public investment",
               q_ii_8_6_3 = "Mobilizing civil society",
               # q_ii_8_7_3 = "International food diplomacy",
               # q_ii_8_8_3 = "Education and awareness-raising",
               # q_ii_8_9_3 = "Innovation and adaptation",
               q_ii_8_96_3 = "Other ( specify )"
  ) %>%  
  tbl_summary(by = dom_3, 
              type= (list=c(q_ii_8_1_3,
                            q_ii_8_2_3,
                            q_ii_8_3_3,
                            q_ii_8_4_3,
                            q_ii_8_5_3,
                            q_ii_8_6_3,
                            # q_ii_8_7_3,
                            # q_ii_8_8_3,
                            # q_ii_8_9_3,
                            q_ii_8_96_3) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_strengths_dom_4=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_4,
                                                                    q_ii_8_1_4,
                                                                    q_ii_8_2_4,
                                                                    q_ii_8_3_4,
                                                                    q_ii_8_4_4,
                                                                    q_ii_8_5_4,
                                                                    q_ii_8_6_4,
                                                                    # q_ii_8_7_4,
                                                                    # q_ii_8_8_4,
                                                                    # q_ii_8_9_4,
                                                                    q_ii_8_96_4
) %>% 
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_8"), as.numeric)) %>% 
  apply_labels(q_ii_8_1_4 = "Coordination and collaboration",
               q_ii_8_2_4 = "Global vision",
               q_ii_8_3_4 = "Strategic direction",
               q_ii_8_4_4 = "Regulations and policies",
               q_ii_8_5_4 = "Public investment",
               q_ii_8_6_4 = "Mobilizing civil society",
               # q_ii_8_7_4 = "International food diplomacy",
               # q_ii_8_8_4 = "Education and awareness-raising",
               # q_ii_8_9_4 = "Innovation and adaptation",
               q_ii_8_96_4 = "Other ( specify )"
  ) %>%  
  tbl_summary(by = dom_4, 
              type= (list=c(q_ii_8_1_4,
                            q_ii_8_2_4,
                            q_ii_8_3_4,
                            q_ii_8_4_4,
                            q_ii_8_5_4,
                            q_ii_8_6_4,
                            # q_ii_8_7_4,
                            # q_ii_8_8_4,
                            # q_ii_8_9_4,
                            q_ii_8_96_4) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```
```{r}
set_gtsummary_theme(theme_gtsummary_compact())

tb_strengths_dom_5=EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(dom_5,
                                                                    q_ii_8_1_5,
                                                                    q_ii_8_2_5,
                                                                    q_ii_8_3_5,
                                                                    q_ii_8_4_5,
                                                                    q_ii_8_5_5,
                                                                    q_ii_8_6_5,
                                                                    # q_ii_8_7_5,
                                                                    # q_ii_8_8_5,
                                                                    # q_ii_8_9_5,
                                                                    q_ii_8_96_5
) %>% 
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>% dplyr::mutate(across(starts_with("q_ii_8"), as.numeric)) %>% 
  apply_labels(q_ii_8_1_5 = "Coordination and collaboration",
               q_ii_8_2_5 = "Global vision",
               q_ii_8_3_5 = "Strategic direction",
               q_ii_8_4_5 = "Regulations and policies",
               q_ii_8_5_5 = "Public investment",
               q_ii_8_6_5 = "Mobilizing civil society",
               # q_ii_8_7_5 = "International food diplomacy",
               # q_ii_8_8_5 = "Education and awareness-raising",
               # q_ii_8_9_5 = "Innovation and adaptation",
               q_ii_8_96_5 = "Other ( specify )"
  ) %>%  
  tbl_summary(by = dom_5, 
              type= (list=c(q_ii_8_1_5,
                            q_ii_8_2_5,
                            q_ii_8_3_5,
                            q_ii_8_4_5,
                            q_ii_8_5_5,
                            q_ii_8_6_5,
                            # q_ii_8_7_5,
                            # q_ii_8_8_5,
                            # q_ii_8_9_5,
                            q_ii_8_96_5) ~ "continuous"),
              
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_strengths_dom_1=tb_strengths_dom_1$table_body[,c("var_label","stat_0","stat_2")]
df_strengths_dom_2=tb_strengths_dom_2$table_body[,c("stat_2")]
df_strengths_dom_3=tb_strengths_dom_3$table_body[,c("stat_2")]
df_strengths_dom_4=tb_strengths_dom_4$table_body[,c("stat_2")]
df_strengths_dom_5=tb_strengths_dom_5$table_body[,c("stat_2")]

df_fc = cbind(df_strengths_dom_1,
              df_strengths_dom_2,
              df_strengths_dom_3,
              df_strengths_dom_4,
              df_strengths_dom_5)

names(df_fc)=c("Strengths of these specific policies/programs/strategies",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
ft = custom_tab(df_fc, header, footer)
#FitFlextableToPage(ft)
ft
```


## strengths of political leadership


```{r}
var_vec = c("q_iii_27_1",
            "q_iii_27_2",
            "q_iii_27_3",
            "q_iii_27_4",
            "q_iii_27_5",
            "q_iii_27_6",
            "q_iii_27_7",
            "q_iii_27_8",
            "q_iii_27_9",
            "q_iii_27_10",
            "q_iii_27_96"
)

label_vec = c("Commitment to food security",
              "Recognition of the importance of family farming in national food production",
              "Management of natural resources",
              "Raising awareness of sustainable agricultural practices",
              "International partnerships",
              "Nutrition programs",
              "Agricultural education programs",
              "Adapting to climate change",
              "Commitment to innovation ",
              "Inclusivity and participation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))

description = tibble(
  name = var_vec,
  label = label_vec
)
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%
  set_variable_labels(.labels = var_labels, .strict = FALSE)

```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
                df_2,
                df_3,
                df_4,
                df_5)

names(df_fc)=c("Inspection frequency",
               "All",
                 "Nutrition, health, and food, security",
                 "Poverty reduction, livelihoods, and jobs",
                 "Gender equality, youth, and social inclusion",
                 "Climate adaptation and mitigation",
                 "Environmental health and biodiversity"
)

# hs <- createStyle(
#   textDecoration = "BOLD", fontColour = "#FFFFFF", fontSize = 12,
#   fontName = "Arial Narrow", fgFill = "#4F80BD"
# )
# 
# write.xlsx(df_fc,
#            file = "Tables Ability to evaluate.xlsx",
#            colNames = TRUE, borders = "rows", headerStyle = hs, sheetName = "Ability to evaluate", append=TRUE
# )

# # Create flextable object
# ft <- flextable(data = df_fc) 
# ft
# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```


\newpage

```{r}
var_vec = c("q_iii_32_1",
            "q_iii_32_2",
            "q_iii_32_3",
            "q_iii_32_4",
            "q_iii_32_5",
            "q_iii_32_6",
            "q_iii_32_7",
            "q_iii_32_96"
)

label_vec = c("Clear commitment to food security through policies and programs to combat hunger and malnutrition",
              "Promotion of sustainable management of natural resources",
              "Encouraging the adoption of sustainable agricultural practices",
              "Cooperation with international organizations",
              "Implementation of nutrition programs",
              "Encouraging innovation in agriculture",
              "Elaboration of policies and programs with stakeholders, such as local communities, civil society organizations and the private sector",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))

description = tibble(
  name = var_vec,
  label = label_vec
)
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%
  set_variable_labels(.labels = var_labels, .strict = FALSE)

```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c("Strengths of political leadership",
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## Strengths of interconnedted network

```{r}
#q_iv_2_* q_iv_6_*
```

```{r}
var_vec = c("q_iv_2_1",
            "q_iv_2_2",
            "q_iv_2_3",
            "q_iv_2_96"
            
)

label_var = c("Strengths of interconnedted network")

label_vec = c("Facilitates the sharing of knowledge, research results and best practices between researchers and institutions",
              "Researcher networks offer training and mentoring opportunities, particularly for young researchers.",
              "Interconnected researchers are better prepared to adapt to rapid changes in their field",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_iv_6_1",
            "q_iv_6_2",
            "q_iv_6_3",
            "q_iv_6_4",
            "q_iv_6_96"
)

label_var = c("Strengths of links with interdisciplinary research on food systems")

label_vec = c("Enables holistic understanding",
              "Promotes the creation of more effective solutions to complex challenges",
              "Enables better management of natural resources",
              "Encourages communication between researchers and experts",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


## strengths of policy/strategy dev process

```{r}
#q_v_2_* q_v_6_*
```

```{r}
var_vec = c("q_v_2_1",
            "q_v_2_2",
            "q_v_2_3",
            "q_v_2_4",
            "q_v_2_5",
            "q_v_2_96"
)

label_var = c("Strengths of the policy/strategy development process")

label_vec = c("Enables a better understanding of the real problems and needs of the populations concerned",
              "Contributes new and innovative ideas",
              "Enhances the transparency and accountability of decision-makers",
              "Creates consensus and coherence between stakeholders",
              "Contributes to social cohesion",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_v_6_1",
            "q_v_6_2",
            "q_v_6_3",
            "q_v_6_4",
            "q_v_6_5",
            "q_v_6_6",
            "q_v_6_96"
)

label_var = c("Strengths of the transparent, evidence-based policy/strategy development process")

label_vec = c("Informed decision-making",
              "Policies and strategies are not developed arbitrarily",
              "Better long-term planning",
              "Fewer errors",
              "Public confidence",
              "Ongoing evaluation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


## strengths of decentralized cap and communication channel

```{r}
#q_vi_2_* q_vi_6_* q_vi_10_*
```


```{r}
var_vec = c("q_vi_2_1",
            "q_vi_2_2",
            "q_vi_2_3",
            "q_vi_2_4",
            "q_vi_2_5",
            "q_vi_2_96"
)

label_var = c("Strengths of decentralized capacity and communication channels between the different administrative levels for implementation at local level")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


```{r}
var_vec = c("q_vi_6_1",
            "q_vi_6_2",
            "q_vi_6_3",
            "q_vi_6_4",
            "q_vi_6_5",
            "q_vi_6_96"
)

label_var = c("Strengths of the implementation of institutional policy changes at sector level")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


```{r}
var_vec = c("q_vi_10_1",
            "q_vi_10_2",
            "q_vi_10_3",
            "q_vi_10_4",
            "q_vi_10_5",
            "q_vi_10_96"
)

label_var = c("Strengths in the context of the extension system, from local NGOs and the private sector, for sector-specific support")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## strengths of monitoring and eval data

```{r}
#q_vii_2_* q_vii_6_*
```

```{r}
var_vec = c("q_vii_2_1",
            "q_vii_2_2",
            "q_vii_2_3",
            "q_vii_2_4",
            "q_vii_2_5",
            "q_vii_2_6",
            "q_vii_2_96"
)

label_var = c("Strengths of the monitoring and evaluation data on policy achievements and outcomes that are integrated into the national statistics collection system")

label_vec = c("Informed decision-making",
              "Policies and strategies are not developed arbitrarily",
              "Better long-term planning",
              "Fewer errors",
              "Public confidence",
              "Ongoing evaluation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_vii_6_1",
            "q_vii_6_2",
            "q_vii_6_3",
            "q_vii_6_4",
            "q_vii_6_5",
            "q_vii_6_6",
            "q_vii_6_96"
)

label_var = c("Strengths of data collection for forecasting and monitoring shocks or threats to food systems")

label_vec = c("Informed decision-making",
              "Policies and strategies are not developed arbitrarily",
              "Better long-term planning",
              "Fewer errors",
              "Public confidence",
              "Ongoing evaluation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


## strengths of decentralization of power

```{r}
#q_viii_2_* q_viii_6_* q_viii_10_*
```

```{r}
var_vec = c("q_viii_2_1",
            "q_viii_2_2",
            "q_viii_2_3",
            "q_viii_2_4",
            "q_viii_2_5",
            "q_viii_2_96"
)

label_var = c("Strengths of the decentralization of powers so that strategies can be immediately adapted or revised according to the local context")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_viii_6_1",
            "q_viii_6_2",
            "q_viii_6_3",
            "q_viii_6_4",
            "q_viii_6_5",
            "q_viii_6_96"
)

label_var = c("Strengths in the context of analysis and development of business and institutional strategies driven by control system data")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


```{r}
var_vec = c("q_viii_10_1",
            "q_viii_10_2",
            "q_viii_10_3",
            "q_viii_10_4",
            "q_viii_10_5",
            "q_viii_10_96"
)

label_var = c("Strengths of the capacity to develop revisions of policy strategies based on the effects of shocks on food production systems")

label_vec = c("Enables policies and programs to be adapted to the specific needs of local communities",
              "Brings decision-making closer to citizens",
              "Enables more efficient management of local resources",
              "Local authorities have the flexibility to react quickly to changing community needs",
              "Helps reduce regional inequalities by investing in disadvantaged areas, encouraging balanced development",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name) 
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## others strengths



## Weaknesses of interconnedted network

```{r}
#q_iv_3_* q_iv_7_*
```

```{r}
var_vec = c("q_iv_3_1",
            "q_iv_3_2",
            "q_iv_3_3",
            "q_iv_3_4",
            "q_iv_3_5",
            "q_iv_3_96"
)

label_var = c("Weaknesses of this interconnected network")

label_vec = c("Some researchers need additional training in collaboration, scientific communication and project management.",
              "Lack of effective coordination within the network, leading to duplication of effort, loss of resources and lack of alignment on common goals.",
              "Limited research funding",
              "Researchers working in remote areas face challenges related to geographic isolation, difficult travel and the costs associated with face-to-face meetings.",
              "Researchers within the network have unequal resources, particularly in terms of access to research infrastructure, funding and equipment.",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_iv_7_1",
            "q_iv_7_2",
            "q_iv_7_3",
            "q_iv_7_4",
            "q_iv_7_96"
)

label_var = c("Weaknesses of links with interdisciplinary research on food systems")

label_vec = c("Some researchers need additional training in collaboration, scientific communication and project management.",
              "Lack of effective coordination within the network, leading to duplication of effort, loss of resources and lack of alignment on common goals.",
              "Limited research funding",
              "Researchers working in remote areas face challenges related to geographic isolation, difficult travel and the costs associated with face-to-face meetings.",
              "Researchers within the network have unequal resources, particularly in terms of access to research infrastructure, funding and equipment.",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## Weaknesses of policy/strategy dev process

```{r}
#q_v_3_* q_v_7_*
```

```{r}
var_vec = c("q_v_3_1",
            "q_v_3_2",
            "q_v_3_3",
            "q_v_3_4",
            "q_v_3_5",
            "q_v_3_96"
)

label_var = c("Weaknesses of policy/strategy development through a participatory and consultative process")

label_vec = c("More complex and time-consuming",
              "Costly in terms of financial, human and logistical resources",
              "The influence of certain powerful players or interest groups seeking to manipulate results in their favor.",
              "The lack of effective participation and negotiation skills among certain stakeholders",
              "Difficulty in communicating and disseminating results and decisions to stakeholders, leading to misunderstandings and dissatisfaction.",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_v_7_1",
            "q_v_7_2",
            "q_v_7_3",
            "q_v_7_4",
            "q_v_7_5",
            "q_v_7_96"
)

label_var = c("Weaknesses of the transparent, evidence-based policy/strategy development process")

label_vec = c("A complex and demanding process in terms of resources, time and coordination",
              "Difficulty in obtaining quality data and reliable evidence",
              "Over-reliance on evidence, delaying decision-making",
              "Lack of technical skills to collect, analyze and interpret data correctly",
              "Selective choice of data or evidence to be used is biased",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## Weaknesses of decentralized cap and communication channel

```{r}
#q_vi_3_* q_vi_7_* q_vi_11_*
```

```{r}
var_vec = c("q_vi_3_1",
            "q_vi_3_2",
            "q_vi_3_3",
            "q_vi_3_96"
)

label_var = c("Weaknesses of the decentralized capacity and of the communication channels between the different administrative levels for implementation at local level")

label_vec = c("Inequalities in performance between different regions",
              "Lack of financial, technical and human resources to effectively implement policies and programs.",
              "Lack of mechanisms to properly monitor and evaluate policy and program implementation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_vi_7_1",
            "q_vi_7_2",
            "q_vi_7_3",
            "q_vi_7_96"
)

label_var = c("weak points in implementing institutional policy changes at sector level")

label_vec = c("Inequalities in performance between different regions",
              "Lack of financial, technical and human resources to effectively implement policies and programs.",
              "Lack of mechanisms to properly monitor and evaluate policy and program implementation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## Weaknesses of monitoring and eval data

```{r}
#q_vii_3_* q_vii_7_*
```

```{r}
var_vec = c("q_vii_3_1",
            "q_vii_3_2",
            "q_vii_3_3",
            "q_vii_3_4",
            "q_vii_3_5",
            "q_vii_3_96"
)

label_var = c("weaknesses of the monitoring and evaluation data on policy achievements and results that are integrated into the national statistics collection system")

label_vec = c("A complex and demanding process in terms of resources, time and coordination",
              "Difficulty in obtaining quality data and reliable evidence",
              "Over-reliance on evidence, delaying decision-making",
              "Lack of technical skills to collect, analyze and interpret data correctly",
              "Selective choice of data or evidence to be used is biased",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_vii_7_1",
            "q_vii_7_2",
            "q_vii_7_3",
            "q_vii_7_4",
            "q_vii_7_5",
            "q_vii_7_96"
)

label_var = c("weaknesses of data collection for forecasting and monitoring shocks or threats to food systems")

label_vec = c("A complex and demanding process in terms of resources, time and coordination",
              "Difficulty in obtaining quality data and reliable evidence",
              "Over-reliance on evidence, delaying decision-making",
              "Lack of technical skills to collect, analyze and interpret data correctly",
              "Selective choice of data or evidence to be used is biased",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## Weaknesses of decentralization of power

```{r}
#q_viii_3_* q_viii_7_* q_viii_11_*
```

```{r}
var_vec = c("q_viii_3_1",
            "q_viii_3_2",
            "q_viii_3_3",
            "q_viii_3_96"
)

label_var = c("weak points in the decentralization of powers, so that strategies can be immediately adapted or revised according to the local context")

label_vec = c("Inequalities in performance between different regions",
              "Lack of financial, technical and human resources to effectively implement policies and programs.",
              "Lack of mechanisms to properly monitor and evaluate policy and program implementation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

```{r}
var_vec = c("q_viii_7_1",
            "q_viii_7_2",
            "q_viii_7_3",
            "q_viii_7_96"
)

label_var = c("weak points in the context of analysis and development of business and institutional strategies driven by control system data")

label_vec = c("Inequalities in performance between different regions",
              "Lack of financial, technical and human resources to effectively implement policies and programs.",
              "Lack of mechanisms to properly monitor and evaluate policy and program implementation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage


```{r}
var_vec = c("q_viii_11_1",
            "q_viii_11_2",
            "q_viii_11_3",
            "q_viii_11_96"
)

label_var = c("weaknesses in the capacity to develop revisions of policy strategies based on the effects of shocks on food production systems")

label_vec = c("Inequalities in performance between different regions",
              "Lack of financial, technical and human resources to effectively implement policies and programs.",
              "Lack of mechanisms to properly monitor and evaluate policy and program implementation",
              "Other ( specify )"
)

df = EVALUATION_DES_CAPACITES_Hema  %>% dplyr::select(domain,var_vec) %>% 
  dplyr::mutate(dom_1=ifelse(dom_1==1,"Yes","No")) %>%
  dplyr::mutate(dom_2=ifelse(dom_2==1,"Yes","No")) %>%
  dplyr::mutate(dom_3=ifelse(dom_3==1,"Yes","No")) %>%
  dplyr::mutate(dom_4=ifelse(dom_4==1,"Yes","No")) %>%
  dplyr::mutate(dom_5=ifelse(dom_5==1,"Yes","No")) %>%
  dplyr::mutate(across(var_vec, as.numeric))
description = tibble(   name = var_vec,   label = label_vec ) 
var_labels <- setNames(as.list(description$label), description$name)
df <- df %>%   set_variable_labels(.labels = var_labels, .strict = FALSE)
```


```{r}

tb_1 = df %>% dplyr::select(dom_1,var_vec
                            
) %>%  
  tbl_summary(by = dom_1,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Nutrition, health, and food, security") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


## domain 2

tb_2=df %>% dplyr::select(dom_2,var_vec
                          
) %>%  
  tbl_summary(by = dom_2,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Poverty reduction, livelihoods, and jobs") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()


tb_3=df %>% dplyr::select(dom_3,var_vec
                          
)  %>%  
  tbl_summary(by = dom_3,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Gender equality, youth, and social inclusion") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_4=df %>% dplyr::select(dom_4,var_vec
                          
)%>%  
  tbl_summary(by = dom_4,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Climate adaptation and mitigation") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

tb_5=df %>% dplyr::select(dom_5,var_vec
                          
) %>%  
  tbl_summary(by = dom_5,
              type= (list=var_vec ~ "continuous"),
              statistic = list(all_continuous() ~ "{mean}"),
              digits = everything() ~ c(2,0), missing = "no") %>%
  modify_header(label = "Environmental health and biodiversity") %>%
  add_overall() %>%
  add_n() %>%  
  add_stat(fns = everything() ~ add_by_n) %>%
  modify_header(starts_with("add_n_stat") ~ "**N**") %>%
  modify_table_body(~ .x %>%
                      dplyr::relocate(add_n_stat_1, .before = stat_1) %>%
                      dplyr::relocate(add_n_stat_2, .before = stat_2)) %>% italicize_labels()

```

```{r}
df_1=tb_1$table_body[,c("var_label","stat_0","stat_2")]
df_2=tb_2$table_body[,c("stat_2")]
df_3=tb_3$table_body[,c("stat_2")]
df_4=tb_4$table_body[,c("stat_2")]
df_5=tb_5$table_body[,c("stat_2")]

df_fc = cbind(df_1,
              df_2,
              df_3,
              df_4,
              df_5)

names(df_fc)=c(label_var,
               "All",
               "Nutrition, health, and food, security",
               "Poverty reduction, livelihoods, and jobs",
               "Gender equality, youth, and social inclusion",
               "Climate adaptation and mitigation",
               "Environmental health and biodiversity"
)

# Set Table header
header <- str_squish(str_remove("Table: ", "\n"))
# Set Table footer
footer <- str_squish(str_remove("", "\n"))
# Set custom_tab() defaults
customtab_defaults()
custom_tab(df_fc, header, footer)
```

\newpage

## others Weaknesses

# Recommendations to improve

## coordination mechanism

```{r}
#q_iii_15_1_*
```


## political leadership

```{r}
#q_iii_29_*
```


## strategic direction by managers

```{r}
#q_iii_34_*
```



```{r}
# Here are variables for which we will have to some text analysis: q_iv_4 // interconnected network
# q_iv_8 // links with interdisplinary research
# q_v_4 // policy/strategy dev through a partiicpatory
# q_v_8 // policy/strategy dev
# q_vi_8 // implementaion of institutional policy changes
# q_vii_4 // monitoring and eval data
# q_vii_8 // data collection
# q_viii_4 // decentralization of powers
# q_viii_8 // analysis and business of development
# q_viii_12 // revisions of pol strategy
# q_ix_4 // staff turnover
# q_ix_14 // incentives to reduce staff turnover
# q_ix_18 // financing
```

